Lipid Interactomics Website

### 2025-01-14 MaintenanceInstructions.qmd
Minor updates, new help symbol
EOD update

---
title: "Maintenance Instructions"
author: "Gaelen Guzman"
date: 2025/01/09
format: 
  html:
    embed-resources: true
standalone: true
---

@@

If you want to add a page, you need to make a new .qmd file in the proper subfolder and render it as an .html file (conveniently, the Preview button in VS Code does that for you, but you can use whatever IDE you want). Then you need to add two lines to the .yml file so that the page is properly linked on the sidebar or navbar (if you don't it'll be unlinked and you'll need to know the whole path to find it, like this maintenance page).

>>>>

---
title: "Maintenance Instructions"
author: "Gaelen Guzman"
date: 2025/01/09
format: 
  html:
    embed-resources: true
standalone: true
meta:
  robots: "noindex"
---

@@

If you want to add a page, you need to make a new .qmd file in the proper subfolder and render it as an .html file (conveniently, the Preview button in VS Code does that for you, but you can use whatever IDE you want). Then you need to add two lines to the .yml file so that the page is properly linked on the sidebar or navbar (first the href to denote the file path to the .html file, then the text to display on the page) -- if you don't add these, the page will remain unlinked and you'll need to know the whole URL to find it (like this maintenance page).

### 2025-01-14 index.qmd
Beginning to overhaul site structure
EOD update

Possible site names:

* CLiP Database -- **C**lickable **Li**pid **P**roteomics Database

* TriP Database -- **Tri**functional lipid **P**roteome Database

* TriLiP Database -- **Tri**functional **L**ipid **P**roteome: A Resource for Trifunctional Lipid-Based Proteomics Data

>>>>

A site map with big buttons leading to each of the lipid classes.
